Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-03 paper/main.tex
paper table

\newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
\begin{table*}[tb]
  \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
  Mean runtime is shown in hours. 
  %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
  \label{tab:results}}
  \resizebox{\textwidth}{!}{%
\begin{tabular}{r@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}
 \toprule
            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
            \bf Problem & \bf     Instance & \mcolc{2}{CEGO} & \mcolc{2}{UMM}   &                         &            & \bf & \bf CEGO       & \bf UMM                       \\\midrule
LOP
& N-p50-01       & 21034.3             & (183.9)            & 21161.8            & (657.4)           & [-606.0,             & 351.0]              & 305.8        & 144.6 & 0.5  \\
& N-p50-02       & 21767.3             & (254.9)            & 21746.6            & (645.4)           & [-458.6,             & 500.0]              & 315.1        & 144.5 & 0.5  \\
& N-t1d100.01    & 78012.0             & (432.1)            & 76499.3            & (1099.7)          & [696.4,              & 2329.0]             & 158.3        & 145.1 & 1.9  \\
& N-t1d100.02    & 78834.0             & (477.8)            & 76860.7            & (864.0)           & [1303.8,             & 2642.8]             & 156.0        & 144.7 & 1.8  \\
& N-atp111       & 668.5               & (9.4)              & 596.6              & (17.0)            & [58.8,               & 85.0]               & 137.9        & 145.1 & 2.3  \\
& N-atp134       & 856.4               & (12.2)             & 760.1              & (23.4)            & [78.4,               & 114.2]              & 116.5        & 145.0 & 3.3  \\
& N-t1d150.01    & 186969.0            & (2094.6)           & 179615.6           & (1731.5)          & [5543.3,             & 9163.5]             & 103.9        & 145.7 & 4.4  \\
& N-t1d150.02    & 183414.7            & (779.2)            & 177524.2           & (1165.6)          & [4949.2,             & 6831.8]             & 103.6        & 145.3 & 4.6  \\
& N-t2d150.01    & 22207.3             & (1667.3)           & 15136.9            & (745.9)           & [5817.1,             & 8323.7]             & 104.5        & 145.5 & 4.5  \\
& N-t2d150.02    & 22036.0             & (744.7)            & 14718.4            & (677.5)           & [6648.3,             & 7986.9]             & 103.1        & 145.0 & 4.5  \\
& N-t1d200.01    & 333804.1            & (1191.9)           & 323501.4           & (1385.7)          & [9086.4,             & 11519.0]            & 77.7         & 145.4 & 7.6  \\
& N-t1d200.02    & 331730.9            & (2819.7)           & 319786.2           & (2265.6)          & [9533.6,             & 14355.8]            & 78.2         & 145.9 & 7.1  \\
& N-t2d200.01    & 54043.6             & (1477.6)           & 33389.0            & (1984.0)          & [19001.4,            & 22307.8]            & 78.2         & 146.7 & 7.4  \\
& N-t2d200.02    & 52787.0             & (4194.2)           & 35589.0            & (2319.6)          & [13948.0,            & 20448.0]            & 78.9         & 145.7 & 7.5  \\
& N-be75np\_150  & 3669753.9           & (74292.3)          & 3216907.1          & (72239.3)         & [383998.5,           & 521695.1]           & 105.2        & 145.5 & 4.4  \\
& N-be75np\_250  & 10818828.5          & (127722.3)         & 9582261.7          & (258176.8)        & [1040022.9,          & 1433110.7]          & 62.5         & 146.4 & 12.5 \\
& N-be75eec\_150 & 1592220.8           & (29945.9)          & 1418578.9          & (56557.7)         & [130141.0,           & 217142.8]           & 103.2        & 145.9 & 4.4  \\
& N-be75eec\_250 & 5098734.4           & (172874.0)         & 4430408.5          & (110233.0)        & [530352.4,           & 806299.4]           & 63.0         & 146.7 & 12.3 \\\midrule
PFSP
& rec05          & 1317.9              & (25.1)             & 1332.5             & (15.6)            & [-34.5,              & 5.3]                & 400.0        & 38.6  & 0.1  \\
& rec13          & 2128.2              & (25.0)             & 2163.6             & (28.1)            & [-60.4,              & -10.4]              & 400.0        & 38.6  & 0.1  \\
& rec19          & 2398.6              & (19.8)             & 2405.2             & (12.8)            & [-22.5,              & 9.3]                & 400.0        & 85.2  & 0.2  \\\midrule
QAP
& nug12          & 624.2               & (26.3)             & 661.2              & (17.8)            & [-58.3,              & -15.7]              & 400.0        & 14.2  & 0.0  \\
& kra30b         & 120192.0            & (1778.1)           & 119923.0           & (3459.6)          & [-2379.5,            & 2917.5]             & 400.0        & 85.1  & 0.2  \\
& tho30          & 192416.0            & (2584.2)           & 191586.4           & (4342.0)          & [-2582.9,            & 4242.1]             & 400.0        & 85.6  & 0.2  \\
& kra30a         & 119872.0            & (1746.7)           & 119502.0           & (1827.5)          & [-1309.8,            & 2049.8]             & 400.0        & 86.1  & 0.2  \\
& nug30          & 7486.8              & (40.4)             & 7472.4             & (83.6)            & [-49.0,              & 77.8]               & 400.0        & 86.5  & 0.2  \\
& kra32          & 115907.0            & (4663.4)           & 116898.0           & (4343.1)          & [-5226.3,            & 3244.3]             & 400.0        & 94.0  & 0.2  \\
\bottomrule
\end{tabular}}
\vspace*{-1em}
 \end{table*}

>>>>

\newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
%\begin{table*}[tb]
%  \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
%  Mean runtime is shown in hours. 
%  %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
%  \label{tab:results}}
%  \resizebox{\textwidth}{!}{%
%\begin{tabular}{r@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}
% \toprule
%            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
%            \bf Problem & \bf     Instance & \mcolc{2}{CEGO} & \mcolc{2}{UMM}   &                         &            & \bf & \bf CEGO       & \bf UMM                       \\\midrule

\begin{table*}[tb] % resumns
\begin{tabular}{l@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}%llrlrllrrr}
\toprule
%Problem &    Instance &  CEGO\_Fitness\_mean & CEGO\_Fitness\_std &  UMM\_Fitness\_mean & UMM\_Fitness\_std &    Confidence interval &  CEGO F. evaluations &  CEGO Runtime &  UMM Runtime \\
            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
            \bf Problem & \bf     Instance & \mcolc{2}{CEGO} & \mcolc{2}{UMM}   &                         &            & \bf & \bf CEGO       & \bf UMM                       \\\midrule
\midrule
    LOP &    N-p40-01 &            10496.6 &          (116.8) &           12369.1 &         (389.9) &     [-2157.1, -1587.9] &                400.0 &          19.9 &          0.3 \\
    LOP &    N-p40-02 &            11714.7 &           (84.7) &           13160.5 &         (454.8) &     [-1773.5, -1118.1] &                400.0 &          20.1 &          0.3 \\
    LOP &  N-t59b11xx &           102408.0 &         (3800.2) &          114075.5 &        (5389.2) &    [-16084.2, -7250.8] &                400.0 &          21.1 &          0.4 \\
    LOP &  N-t59d11xx &            12692.2 &         (1097.9) &           16662.9 &        (2155.3) &     [-5618.5, -2322.9] &                400.0 &          21.2 &          0.4 \\
    LOP &    N-p50-02 &            19090.5 &          (285.4) &           21746.6 &         (645.4) &     [-3140.6, -2171.6] &                400.0 &          22.9 &          0.5 \\
    LOP &    N-p50-01 &            18197.7 &          (225.6) &           21161.8 &         (657.4) &     [-3447.4, -2480.8] &                400.0 &          23.2 &          0.5 \\
    LOP &  N-sgb75.01 &          1893533.2 &        (28594.6) &         1992059.9 &       (40235.7) &  [-131577.1, -65476.3] &                400.0 &          33.2 &          1.0 \\
    LOP &  N-sgb75.02 &          1895801.8 &        (82847.9) &         1967132.3 &       (49228.1) &   [-136421.2, -6239.8] &                400.0 &          33.3 &          1.1 \\
   PFSP &       rec05 &             1276.2 &           (15.1) &            1276.3 &           (8.4) &          [-11.8, 11.6] &                400.0 &          18.3 &          0.1 \\
   PFSP &       rec13 &             1992.9 &           (27.6) &            2057.8 &          (22.8) &         [-88.8, -41.0] &                400.0 &          18.5 &          0.1 \\
   PFSP &       rec19 &             2264.5 &           (45.0) &            2304.8 &          (37.7) &          [-79.4, -1.2] &                400.0 &          18.2 &          0.2 \\
   PFSP &       rec31 &             3415.5 &           (62.1) &            3419.3 &          (37.0) &          [-52.6, 45.0] &                400.0 &          23.1 &          0.5 \\
\bottomrule
\end{tabular} 
\end{table*}

\begin{table*}[tb]%time
\begin{tabular}{llrrrrrr}
\toprule
Problem &    Instance &  CEGO\_inv &  CEGO\_orig &  UMM\_100 &  UMM\_200 &  UMM\_400 &  UMM\_no\_inv \\
\midrule
    LOP &  N-t59b11xx &   1265.98 &    1240.36 &     1.37 &     5.78 &    22.24 &       21.89 \\
    LOP &  N-t59d11xx &   1269.93 &    1252.89 &     1.37 &     5.62 &    21.84 &       22.30 \\
    LOP &    N-p40-01 &   1195.90 &    1170.81 &     1.14 &     4.61 &    18.13 &       19.06 \\
    LOP &    N-p40-02 &   1207.24 &    1183.09 &     1.15 &     4.76 &    18.11 &       19.06 \\
    LOP &    N-p50-01 &   1391.55 &        NaN &      NaN &      NaN &    27.36 &         NaN \\
    LOP &    N-p50-02 &   1372.71 &        NaN &      NaN &      NaN &    28.36 &         NaN \\
    LOP &  N-sgb75.01 &   1994.22 &    2004.70 &     3.97 &    15.77 &    62.75 &       65.40 \\
    LOP &  N-sgb75.02 &   1995.09 &    1975.41 &     4.03 &    15.90 &    64.58 &       62.69 \\
   PFSP &       rec05 &   1099.63 &     917.81 &     0.30 &     1.14 &     4.54 &        4.53 \\
   PFSP &       rec13 &   1109.51 &    1043.08 &     0.31 &     1.07 &     4.55 &        4.50 \\
   PFSP &       rec19 &   1090.06 &    1087.38 &     0.63 &     2.59 &    10.51 &       10.35 \\
   PFSP &       rec31 &   1387.09 &    1367.26 &     1.79 &     6.90 &    27.84 &       26.91 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[tb]%fitness
\begin{tabular}{llrrrrrr}
\toprule
Problem &    Instance &   CEGO\_inv &   CEGO\_orig &   UMM\_400 &   UMM\_200 &   UMM\_100 &   UMM\_no\_inv \\
\midrule
    LOP &  N-t59b11xx &          102408.0 &           126204.0 &         114075.5 &         115941.5 &         128195.5 &            138819.5 \\
    LOP &  N-t59d11xx &           12692.2 &            30199.8 &          16662.9 &          22117.4 &          28050.4 &             42971.2 \\
    LOP &    N-p40-01 &           10496.6 &            15027.7 &          12369.1 &          13043.7 &          14459.3 &             16471.5 \\
    LOP &    N-p40-02 &           11714.7 &            15150.2 &          13160.5 &          13923.2 &          15027.7 &             16330.7 \\
    LOP &    N-p50-01 &           18197.7 &                NaN &          21161.8 &              NaN &              NaN &                 NaN \\
    LOP &    N-p50-02 &           19090.5 &                NaN &          21746.6 &              NaN &              NaN &                 NaN \\
    LOP &  N-sgb75.01 &         1893533.2 &          2095899.6 &        1992059.9 &        2011271.7 &        2074111.6 &           2111368.5 \\
    LOP &  N-sgb75.02 &         1895801.8 &          2069286.9 &        1967132.3 &        2011004.2 &        2045556.5 &           2056681.8 \\
   PFSP &       rec05 &            1276.2 &             1318.7 &           1276.3 &           1283.1 &           1300.4 &              1332.5 \\
   PFSP &       rec13 &            1992.9 &             2096.0 &           2057.8 &           2113.6 &           2134.9 &              2163.6 \\
   PFSP &       rec19 &            2264.5 &             2328.4 &           2304.8 &           2346.5 &           2392.4 &              2405.2 \\
   PFSP &       rec31 &            3415.5 &             3512.3 &           3419.3 &           3438.9 &           3511.9 &              3554.1 \\
\bottomrule
\end{tabular}
\end{table*}
